We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-04-20 paper/paper.tex
updated table
updated tables
new plots in paper
updated figures

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
Plane width (kpc) & $63.64$ & $19.34$ & $55.78\pm10.65$ & $38.60\pm8.19$ & $0.74$ & $-4.45$\\\hline
$c/a$ ratio & $0.42$ & $0.18$ & $0.51\pm0.11$ & $0.45\pm0.12$ & $-0.87$ & $-2.75$\\\hline
$b/a$ ratio & $0.96$ & $0.87$ & $0.82\pm0.08$ & $0.83\pm0.08$ & $1.74$ & $0.67$\\\hline
  \end{tabular}
  \caption{Results from observations with $N_s=11$. 
    for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the standard deviation of the randomized data. \label{table:observations}}
\end{table*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
\caption{Plane width characterization in observations and
  simulations (Illustris-1-Dark in this case). In all panels the
  horizontal/vertical axis corresponds to the  M31/MW or the
  most/less massive halo in the pair. 
  Left. Plane width in physical units comparing the results from observations
(stars) against the result of spherically randomizing the satellite
positions (circles). 
Middle. Average from the observations (star) and the average from each
pair in the simulation (circles).
Right. Same as the middle panel except that this time each point has
been normalized (median substracted and normalized by the standard
deviation) to the results of its randomization. 
The main message of these panels is that the MW has a significantly
thinner plane both compared to the result of its own satellite
spherical randomization (left panel) and the expectation from
simulations (middle and right panel).  
This low value is $2\sigma$ away from what is expected in a spherical
distribution. 
In M31 the satellite distribution is in agreement with the
expectations both from a spherical distribution and the results from the
simulations. 
\label{fig:scatter_width}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The same message holds in this case; namely, that 
the MW has a significantly lower $c/a$ value than the
expectation from the spherical distribution and from the simulations. 
This low value is also $2\sigma$ away from the expactations for a
spherical distribution.
On the other hand, M31 is consistent both with a spherical
distribution and with the results from simulations.
\label{fig:scatter_ca_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_ba_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and 
the simulations. 
\label{fig:scatter_ba_ratio}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.47\textwidth]{expected_numbers_n_M31.pdf}
\includegraphics[width=0.47\textwidth]{expected_numbers_n_MW.pdf}
\caption{Probability distribution for the expected number of M31 and
  MW halos showing the same degree of atypicality as the Local Group if drawn
  from a sample of $10^4$ isolated pairs. 
  The distributions correspond to results derived from Illustris-1-Dark, Illustris,
  and ELVIS data.
  In the most optimistic case (Illustris-1-Dark), $1\%$ of the pairs have
  two halos with properties similar to the LG. 
  In the case of Illustris-1 this percentage drops to $0.1\%$ and
  $0.01\%$ for ELVIS. 
\label{fig:expected_number}}
\end{figure*}

>>>>

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
lane width (kpc) & $63.64$ & $19.34$ & $56.74\pm10.96$ & $37.56\pm7.90$ & $0.63$ & $-2.31$\\\hline
$c/a$ ratio & $0.42$ & $0.18$ & $0.53\pm0.11$ & $0.46\pm0.11$ & $-1.00$ & $-2.46$\\\hline
$b/a$ ratio & $0.96$ & $0.87$ & $0.81\pm0.08$ & $0.80\pm0.09$ & $1.69$ & $0.80$\\\hline
  \end{tabular}
  \caption{Results from observations with $N_s=11$. 
    for the different
    quantities describing the satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the standard deviation of the randomized data. \label{table:observations}}
\end{table*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11.pdf}
\caption{Plane width characterization in observations and
  simulations (Illustris-1-Dark in this case). In all panels the
  horizontal/vertical axis corresponds to the  M31/MW or the
  most/less massive halo in the pair. 
  Left. Plane width in physical units comparing the results from observations
(stars) against the result of spherically randomizing the satellite
positions (circles). 
Middle. Average from the observations (star) and the average from each
pair in the simulation (circles).}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_M31_n_11_normed.pdf}
\includegraphics[width=0.48\textwidth]{input_illustris1dark_obs_MW_n_11_normed.pdf}
\caption{Right. Same as the middle panel except that this time each point has
been normalized (median substracted and normalized by the standard
deviation) to the results of its randomization. 
The main message of these panels is that the MW has a significantly
thinner plane both compared to the result of its own satellite
spherical randomization (left panel) and the expectation from
simulations (middle and right panel).  
This low value is $2\sigma$ away from what is expected in a spherical
distribution. 
In M31 the satellite distribution is in agreement with the
expectations both from a spherical distribution and the results from the
simulations. }
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{LG_numbers.pdf}
\includegraphics[width=0.32\textwidth]{M31_numbers.pdf}
\includegraphics[width=0.32\textwidth]{MW_numbers.pdf}
\caption{Probability distribution for the expected number of M31 and
  MW halos showing the same degree of atypicality as the Local Group if drawn
  from a sample of $10^4$ isolated pairs. 
  The distributions correspond to results derived from Illustris-1-Dark, Illustris,
  and ELVIS data.
  In the most optimistic case (Illustris-1-Dark), $1\%$ of the pairs have
  two halos with properties similar to the LG. 
  In the case of Illustris-1 this percentage drops to $0.1\%$ and
  $0.01\%$ for ELVIS. 
\label{fig:expected_number}}
\end{figure*}
